---
title: "Heterogeneous effects analysis of conjoint experiments"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{cjbart-demo}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This vignette provides a brief example of how to estimate heterogeneous effects in conjoint experiments, using \code{cjbart}.

Suppose we conducted a conjoint experiment on 500 individuals, where each individual makes 5 discrete choices between two profiles. The resultant dataframe would include 2500 observations. within this conjoint, suppose there are five attributes A-E, each with 3 levels. We also record two covariates of each subject. Let's mock up this data:

```{r data, include=TRUE}
subjects <- 500
rounds <- 5
obs <- subjects*rounds

fake_data <- data.frame(id1 = rep(1:subjects, each=rounds),
                        Y = sample(c(1,0), obs, replace = TRUE),
                        A = sample(c("a1","a2","a3"), obs, replace = TRUE),
                        B = sample(c("b1","b2","b3"), obs, replace = TRUE),
                        C = sample(c("c1","c2","c3"), obs, replace = TRUE),
                        D = sample(c("d1","d2","d3"), obs, replace = TRUE),
                        E = sample(c("e1","e2","e3"), obs, replace = TRUE),
                        covar1 = rep(runif(subjects, 0 ,100), 
                                     each = rounds),
                        covar2 = rep(sample(c(1,0), subjects, replace = TRUE), 
                                     each = rounds),
                        stringsAsFactors = TRUE)
```

## Train a probit BART model on conjoint data

To estimate a conjoint model on this data we will use the `cjbart()` function, which uses Bayesian Additive Regression Trees (BART) to approximate the relationships between the outcome (a binary choice), the randomised attribute-levels, and the included covariates. The result is a `pbart` model, which we will use to estimate heterogeneity in the treatment effects:

```{r train, include=TRUE}
library(cjbart)
cj_model <- cjbart(data = fake_data,
                   Y_var = "Y", 
                   id_var = "id1")

```

To generate heterogeneity estimates at the observation- and individual-level, we use the `OMCE()` function. We pass in both the original experimental data, and the conjoint model generated in the last step. At this point, we also declare the names of the conjoint attribute variables (`attribs`) and the reference category we want to use for each attribute when calculating the marginal component effects (`ref_levels`). The vector of reference levels must be of the same length as `attribs`, with the level at position `i` corresponding to the `attrib[i]`:

```{r OMCE, include=TRUE}
het_effects <- cjbart::OMCE(data = fake_data, 
                            model = cj_model, 
                            attribs = c("A","B","C","D","E"),
                            ref_levels = c("a1","b1","c1","d1","e1"),
                            Y_var = "Y", 
                            id_var = "id1", 
                            cores = 1)
```


<!-- # We can see the predictions by running: -->
<!-- predicted_omces$results -->

<!-- ## Then, recover IMCEs -->
<!-- predicted_imces <- IMCE(predicted_omces, id = "id1") -->

<!-- # Again, we can see the results by running: -->
<!-- predicted_imces$results -->

<!-- ## Then plot OMCEs or IMCES: -->
<!-- plot_omce(predicted_omces, "covar2") -->
